Transformer-Based Reranking \\for Improving Korean Morphological Analysis System

### 2023-12-29 contents/draft.tex
Minor update for HM Sweetie and nash
staring position -> starting positions

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=1.0\textwidth]{fig;lattice-v3}}
        \caption{An illustrated example of a constructed lattice, the best-decoded result, and a set of the generated secondary paths. A lattice is constructed by restricting a set of nodes by morpheme lexicon, where each node is marked by its ``rank'' among a set of morphemes whose staring position are the same each other. The best path indicates the sequence of top-1 nodes in the lattice, i.e., nodes marked by the 1st rank. A secondary path is generated by replacing a top-1 node with the next top node at the same starting position, which is marked by the 2nd rank. }
        \label{fig:lattice}
    \end{figure*}

>>>>

    \begin{figure*}[ht]
        \centerline{\includegraphics[width=1.0\textwidth]{fig;lattice-v3}}
        \caption{An illustrated example of a constructed lattice, the best-decoded result, and a set of the generated secondary paths. A lattice is constructed by restricting a set of nodes by morpheme lexicon, where each node is marked by its ``rank'' among a set of morphemes whose starting positions are the same each other. The best path indicates the sequence of top-1 nodes in the lattice, i.e., nodes marked by the 1st rank. A secondary path is generated by replacing a top-1 node with the next top node at the same starting position, which is marked by the 2nd rank.}
        \label{fig:lattice}
    \end{figure*}
